### 2014-02-18 etc/abstract.tex
shift to do-fewer

Explain why Random

>>>>

% 1.Statetheproblem
Mutation analysis is a metric for measuring the quality of test suites. However, its exorbitant computational requirements makes it hard to use in practice. Choosing a smaller subset of mutations to run is a simple approach that can alleviate this problem.

%2.Saywhyit’saninterestingproblem
However, how best to choose among multiple selection criterias is an open problem, especially for real-world programs and test-suites.

%3.Saywhatyoursolutionachieves
Our research compare a number of selection criteria along different dimensions including prediction of original mutation score, mutant reduction ratio, and time for completion.

%4.Saywhatfollowsfromyoursolution
